The KMOS Deep Survey (KDS): dynamical measurements of $z\sim3.5$ main sequence galaxies\thanks{Based on observations obtained at the Very Large Telescope of the European Southern Observatory. Programme IDs: }

### 2017-03-29 paper.tex
Removed half-light plot

In the right panel of Figure \ref{fig:morpho-distributions} we plot the distribution of the derived $R_{1/2}$ values (for the 28 galaxies with {\em HST} imaging in the refined sample, \cref{subsubsec:kin_sample_summary}) in comparison to the reference samples spanning two redshift ranges.
In general the KDS galaxies are much more compact than at lower redshift and overlap with the smaller side of the $3 < z < 4$ reference sample, which we attribute to the lack of massive galaxies in the KDS sample (through the mass-size relation \citep[e.g.][]{Trujillo2004}).

@@

\begin{figure*}
    \centering \hspace{-2.0cm}
    \begin{subfigure}[h!]{0.50\textwidth}
        \centering
        \includegraphics[height=3.5in]{axis_ratio_distributions.png}
        %\caption{axis ratio distributions}
    \end{subfigure} \hspace{0.4cm}
    \begin{subfigure}[h!]{0.50\textwidth}
        \centering
        \includegraphics[height=3.6in]{size_distributions.png}
        %\caption{size distributions}
    \end{subfigure}
    \caption{{\it Left:} The normalised counts of KDS galaxies in bins of axis ratio is plotted, along with the normalised counts from the morphological catalogue presented in \protect\cite{VanderWel2012} in two redshift ranges.
    The axis ratio distribution appears to be constant with time as traced by the reference samples, and the KDS values are in good agreement with a relatively uniform distribution spanning $0.3 < b/a < 0.9$.
    This suggests that we are not biased towards deriving a particular value for the axis ratio.
    {\it Right:} The normalised counts of KDS galaxies in bins of half-light radius is plotted, along with the half-light radii of the same \protect\cite{VanderWel2012} galaxies as the left panel.
    We find that the KDS galaxies are much more compact than those at low redshift, as traced by $R_{1/2}$ measure, which could partially be explained by the F160W filter tracing a younger stellar population at $z\simeq3.5$.
    The distribution of KDS $R_{1/2}$ values is consistent with the smaller part of the distribution in the high redshift reference sample, which we attribute to the lack of very massive galaxies in the KDS sample.
    The extracted velocity values are not sensitive to the exact value of the half-light radius, as the intrinsic rotation curves flatten at small radii (see \protect\ref{fig:main_body_kinematic_grids}).}
    \label{fig:morpho-distributions}
\end{figure*}

@@

\begin{equation}\label{eq:owen_sigma}
\sigma_{int} = \sqrt{\left(\sigma_{obs} - \sigma_{BS}^{2}\right) - \sigma_{inst}^{2}}
\end{equation}

@@

@@

\subsubsection{Kinematic and photometric axes}\label{subsubsection:kin_and_phot}

The dynamical model parameter $PA_{Kin}$ can be compared with $PA_{morph}$ computed by {\tt GALFIT} in \cref{subsubsec:galfitting} to indicate the degree of misalignment between the gaseous and stellar components of the galaxies.
This follows the analysis described in \citep[e.g.][]{Epinat2008,Epinat2012,Barrera-Ballesteros2014,Barrera-Ballesteros2015,Wisnioski2015,Harrison2017,Swinbank2017} where rotating galaxies generally have $\Delta PA \equiv |PA_{kin}-PA_{morph}| < 20^{\circ}$, with the discrepancy increasing as a function of axis ratio due to $PA_{morph}$ becoming more difficult to measure as the galaxy becomes more `face-on'.
Significant misalignment between the two axes can be a signature of galaxy interaction.

This has been discussed in \cite{Hung2015}, where redshifted local interacting galaxies are misclassified as single rotating disks on the basis of their kinematics. 
In short, the galaxies with multiple photometric components do not always have disordered kinematics and so the kinematics alone are not sufficient for classification.
It is difficult to distinguish in some cases between two {\em HST} components rotating together in a single disk (i.e. clumpy disk galaxies e.g. \citealt{Elmegreen2004,Bournaud2007}) with a receding and approaching side and two [O~{\sc III}]$\lambda$5007 emitting blobs which are offset along the line of sight.
Perhaps the most telling diagnostic are two flux peaks in the object spectrum at the kinematic centre viewed in combination with a double peak in the high-resolution imaging flux map. \\

@@

\subsection{The origin and impact of increased velocity dispersions at high redshift}\label{discussion_increase_in_sigma}
Previous studies have claimed that the elevated velocity dispersions observed at high redshift are a consequence of both internal and external processes.
\cite{Law2009} observe galaxies with elevated velocity dispersions at $z\simeq2.2$ (see Figure \ref{fig:sigma_and_v_sigma_w_redshift}) and attribute this to gravitational instabilities following efficient accretion, which can occur when the cold gas becomes dynamically dominant.
\cite{Genzel2011} show that for dispersion-dominated galaxies, the scales susceptible to gravitational collapse are of order the galactic half-light radius. 
Systems such as these form highly unstable and roughly spherical stellar distributions with large internal motions at early times, before more gradual accretion from the galactic halo forms an extended, stable, gaseous disk which instigates kinematic order \citep{Law2009,Genzel2011}.
The physical mechanisms responsible for the increase in $\sigma_{int}$ may also result in a reduction in the observed rotational velocities by partially compensating the gravitational force throughout the galactic disk \citep[e.g.][]{Burkert2010,Wuyts2016b,Ubler2017,Genzel2017,Lang2017}.
Following this, $\sigma_{int}$ decreases over time as ordered rotations begin to dominate and pressure support becomes increasingly insignificant \citep[e.g.][]{Burkert2010,Ubler2017,Genzel2017,Lang2017}.
This is in line with the evolution of gas fractions observed at intermediate and high redshifts \citep[e.g.][]{Saintonge2013,Tacconi2013,Tacconi2017}, with the gas reservoirs of galaxies fed by the accretion of cold gas.

>>>>

%In the right panel of Figure \ref{fig:morpho-distributions} we plot the distribution of the derived $R_{1/2}$ values (for the 28 galaxies with {\em HST} imaging in the refined sample, \cref{subsubsec:kin_sample_summary}) in comparison to the reference samples spanning two redshift ranges.
%In general the KDS galaxies are much more compact than at lower redshift and overlap with the smaller side of the $3 < z < 4$ reference sample, which we attribute to the lack of massive galaxies in the KDS sample (through the mass-size relation \citep[e.g.][]{Trujillo2004}).

@@

\begin{figure}
\centering \hspace{-1.13cm}
\includegraphics[width=0.49\textwidth]{axis_ratio_distributions.png}
\caption{The normalised counts of KDS galaxies in bins of axis ratio is plotted, along with the normalised counts from the morphological catalogue presented in \protect\cite{VanderWel2012} in two redshift ranges.
    The axis ratio distribution appears to be constant with time as traced by the reference samples, and the KDS values are in good agreement with a relatively uniform distribution spanning $0.3 < b/a < 0.9$.
    This suggests that we are not biased towards deriving a particular value for the axis ratio.}
\label{fig:morpho-distributions}
\end{figure}

%\begin{figure*}
%    \centering \hspace{-2.0cm}
%    \begin{subfigure}[h!]{0.50\textwidth}
%        \centering
%        \includegraphics[height=3.5in]{axis_ratio_distributions.png}
%        %\caption{axis ratio distributions}
%    \end{subfigure} \hspace{0.4cm}
%    \begin{subfigure}[h!]{0.50\textwidth}
%        \centering
%        \includegraphics[height=3.6in]{size_distributions.png}
%        %\caption{size distributions}
%    \end{subfigure}
%    \caption{{\it Left:} The normalised counts of KDS galaxies in bins of axis ratio is plotted, along with the normalised counts from the morphological catalogue presented in \protect\cite{VanderWel2012} in two redshift ranges.
%    The axis ratio distribution appears to be constant with time as traced by the reference samples, and the KDS values are in good agreement with a relatively uniform distribution spanning $0.3 < b/a < 0.9$.
%    This suggests that we are not biased towards deriving a particular value for the axis ratio.
%    {\it Right:} The normalised counts of KDS galaxies in bins of half-light radius is plotted, along with the half-light radii of the same \protect\cite{VanderWel2012} galaxies as the left panel.
%    We find that the KDS galaxies are much more compact than those at low redshift, as traced by $R_{1/2}$ measure, which could partially be explained by the F160W filter tracing a younger stellar population at $z\simeq3.5$.
%    The distribution of KDS $R_{1/2}$ values is consistent with the smaller part of the distribution in the high redshift reference sample, which we attribute to the lack of very massive galaxies in the KDS sample.
%    The extracted velocity values are not sensitive to the exact value of the half-light radius, as the intrinsic rotation curves flatten at small radii (see \protect\ref{fig:main_body_kinematic_grids}).}
%    \label{fig:morpho-distributions}
%\end{figure*}

@@

\begin{equation}\label{eq:owen_sigma}
\sigma_{int} = \sqrt{\left(\sigma_{obs} - \sigma_{BS}^{2}\right) - \sigma_{inst}^{2}}
\end{equation} \\

@@

\subsubsection{Kinematic and photometric axes}\label{subsubsection:kin_and_phot}
The dynamical model parameter $PA_{Kin}$ can be compared with $PA_{morph}$ computed by {\tt GALFIT} in \cref{subsubsec:galfitting} to indicate the degree of misalignment between the gaseous and stellar components of the galaxies.
This follows the analysis described in \citep[e.g.][]{Epinat2008,Epinat2012,Barrera-Ballesteros2014,Barrera-Ballesteros2015,Wisnioski2015,Harrison2017,Swinbank2017} where rotating galaxies generally have $\Delta PA \equiv |PA_{kin}-PA_{morph}| < 20^{\circ}$, with the discrepancy increasing as a function of axis ratio due to $PA_{morph}$ becoming more difficult to measure as the galaxy becomes more `face-on'.
Significant misalignment between the two axes can be a signature of galaxy interaction.

This has been discussed in \cite{Hung2015}, where redshifted local interacting galaxies are misclassified as single rotating disks on the basis of their kinematics. 
In short, the galaxies with multiple photometric components do not always have disordered kinematics and so the kinematics alone are not sufficient for classification.
It is difficult to distinguish in some cases between two {\em HST} components rotating together in a single disk (i.e. clumpy disk galaxies e.g. \citealt{Elmegreen2004,Bournaud2007}) with a receding and approaching side and two [O~{\sc III}]$\lambda$5007 emitting blobs which are offset along the line of sight.
Perhaps the most telling diagnostic are two flux peaks in the object spectrum at the kinematic centre viewed in combination with a double peak in the high-resolution imaging flux map.

@@

@@

\subsection{The origin and impact of increased velocity dispersions at high redshift}\label{discussion_increase_in_sigma}
Previous studies have claimed that the elevated velocity dispersions observed at high redshift are a consequence of both internal and external processes.
\cite{Law2009} observe galaxies with elevated velocity dispersions at $z\simeq2.2$ (see Figure \ref{fig:sigma_and_v_sigma_w_redshift}) and attribute this to gravitational instabilities following efficient accretion, which can occur when the cold gas becomes dynamically dominant.

\cite{Genzel2011} show that for dispersion-dominated galaxies, the scales susceptible to gravitational collapse are of order the galactic half-light radius. 
Systems such as these form highly unstable and roughly spherical stellar distributions with large internal motions at early times, before more gradual accretion from the galactic halo forms an extended, stable, gaseous disk which instigates kinematic order \citep{Law2009,Genzel2011}.
The physical mechanisms responsible for the increase in $\sigma_{int}$ may also result in a reduction in the observed rotational velocities by partially compensating the gravitational force throughout the galactic disk \citep[e.g.][]{Burkert2010,Wuyts2016b,Ubler2017,Genzel2017,Lang2017}.
Following this, $\sigma_{int}$ decreases over time as ordered rotations begin to dominate and pressure support becomes increasingly insignificant \citep[e.g.][]{Burkert2010,Ubler2017,Genzel2017,Lang2017}.
This is in line with the evolution of gas fractions observed at intermediate and high redshifts \citep[e.g.][]{Saintonge2013,Tacconi2013,Tacconi2017}, with the gas reservoirs of galaxies fed by the accretion of cold gas.
